The Ranked Nearest Neighbour Interchange space

### 2019-06-27 paper.tex
@lenacoll please make \mrca \parent etc. to use \mathrm or similar, throughout the paper

Furthermore, we will identify leaves by their labels and might call them \emph{taxa} (singular: \emph{taxon}).
For a tree $T$ a subtree consisting of an internal node with both children being leaves is called \emph{cherry}.
An edge $e$ that has no leaf as child is an \emph{internal edge} and we say an edge $e=(u,v)$ has \emph{length} $l$ if $|rank(v) - rank(u)| = l$.
Each internal node $v$ gives a \emph{cluster} $C$ that is the set of taxa descending from this node. \todo{OK?}
We then say that $v$ induces the cluster $C$.
Note that all trees on $n$ taxa share the cluster $\{1,\ldots,n\}$ induced by the root.
A \emph{split} is a bipartition of the taxon set $X$ into sets $A,B$ such that there is an edge $e$ whose deletion results in two trees with taxon sets $A$ and $B$, respectively.
Such a split will be denoted by $A|B$ and we say that it is induced by edge $e$.
Given a subset $S$ of the set of taxa $X$, the \emph{most recent common ancestor} $mrca(S)$ of $S$ is the internal node with lowest rank that is ancestor of all taxa in $S$. \todo{OK?}
In particular, for a single taxon $x \in X$, $mrca(\{x\})$ is the parent of $x$ and will be denoted by $parent(x)$.
We write $mrca_T(S)$ to emphasise that we consider the most recent common ancestor of set $S$ in tree $T$.
Two trees are called \emph{isomorphic} if the underlying rooted phylogenetic trees are isomorphic and the isomorphism preserves ranks of the nodes.

>>>>

Furthermore, we will identify leaves by their labels and might call them \emph{taxa} (singular: \emph{taxon}).
For a tree $T$ a subtree consisting of an internal node with both children being leaves is called a \emph{cherry}.
An edge $e$ that has no leaf as child is an \emph{internal edge} and we say an edge $e=(u,v)$ has \emph{length} $l$ if $|rank(v) - rank(u)| = l$.
Each internal node $v$ gives a \emph{cluster} $C$ that is the set of taxa descending from this node. \todo{OK?}
We then say that $v$ induces the cluster $C$.
Note that all trees on $n$ taxa share the cluster $\{1,\ldots,n\}$ induced by the root.
A \emph{split} is a bipartition of the taxon set $X$ into sets $A,B$ such that there is an edge $e$ whose deletion results in two trees with taxon sets $A$ and $B$, respectively.
Such a split will be denoted by $A|B$ and we say that it is induced by edge $e$.
Given a subset $S$ of the set of taxa $X$, the \emph{most recent common ancestor} $mrca(S)$ of $S$ is the internal node with lowest rank that is ancestor of all taxa in $S$. \todo{OK?}
In particular, for a single taxon $x \in X$, $\mrca(\{x\})$ is the parent of $x$ and will be denoted by $\parent(x)$.
We write $\mrca_T(S)$ to emphasise that we consider the most recent common ancestor of set $S$ in tree $T$.
Two trees are called \emph{isomorphic} if the underlying rooted phylogenetic trees are isomorphic and the isomorphism preserves ranks of the nodes.
